```{r}
library(tidyverse)
```

```{r}

data = read.csv("actions_under_antiquities_act.csv")
data
```

```{r}
dataPre1960 = data[data$year<1950,]
dataPost1960 = data[data$year>1950,]

dataPre1960$acres_affected = as.numeric(dataPre1960$acres_affected)


dataPre1960 <- dataPre1960 %>%
  dplyr::select(states,acres_affected) %>%
  mutate(states = tolower(states)) %>%
  arrange(states) %>%
  group_by(states) %>%
  summarize(mean = mean(acres_affected,na.rm = T))

state_data <- data_frame(state.name) %>%
  mutate(state.name = tolower(state.name)) %>%
  right_join(dataPre1960, by = c("state.name" = "states"))

state_borders <- map_data("state") %>%
  left_join(state_data, by = c("region" = "state.name"))


ggplot(state_borders, aes(x = long, y = lat, fill = as.numeric(mean))) + 
  geom_polygon(aes(group = group), color = "black") + 
  theme_void() + 
  coord_map("polyconic") + 
  scale_fill_gradient2(high = "brown", low = "purple",
                       mid = "white") +
  labs(title = "Average Acres Affected per State, Before 1960",
       fill = "Average Acres Affected") +
  theme(legend.position = "bottom")


dataPost1960$acres_affected = as.numeric(dataPost1960$acres_affected)


dataPost1960 <- dataPost1960 %>%
  dplyr::select(states,acres_affected) %>%
  mutate(states = tolower(states)) %>%
  arrange(states) %>%
  group_by(states) %>%
  summarize(mean = mean(acres_affected,na.rm = T))


state_data <- data_frame(state.name) %>%
  mutate(state.name = tolower(state.name)) %>%
  right_join(dataPost1960, by = c("state.name" = "states"))

state_borders <- map_data("state") %>%
  left_join(state_data, by = c("region" = "state.name"))


ggplot(state_borders, aes(x = long, y = lat, fill = as.numeric(mean))) + 
  geom_polygon(aes(group = group), color = "black") + 
  theme_void() + 
  coord_map("polyconic") + 
  scale_fill_gradient2(high = "brown", low = "purple",
                       mid = "white") +
  labs(title = "Average Acres Affected per State, After 1960",
       fill = "Average Acres Affected") +
  theme(legend.position = "bottom")
```

The pre-1960 map displays the average number of acres affected in each state. We see an abundance of acres affected primarily in the mid-western region, and south-east. There seems to be a lot of acres affected specifically in Nevada and Ohio.
The post-1960 map shows an increase in activity in the northeastern region, with acres affected still also being part of the midwestern region. Maine seems to be a primary source of affected acres.



